\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-01 journalWallFriction/Experiment.tex
edited the paper!

 The magnetic manipulation system has two pairs of electromagnetic coils each with iron cores at their centers, and arranged orthogonal to each other. The iron core at the center of each coil concentrates the magnetic field towards the workspace. An Arduino and four SyRen regenerative motor drivers were used for control inputs to the coils. Finally, a FOculus F0134SB 659 x 494 pixel camera was attached to the top of the system focusing on the workspace which was back-lit by a 15$w$ LED light strip.

@@

The intestine phantom model was used as the first test field of the project and was made to mimic the geometry of an intestine and its villi. The model consists of a circular ring with an outer diameter of $\SI{50}{\milli\metre}$, an inner diameter of $\SI{46}{\milli\metre}$, and 60 $\SI{2}{\milli\metre}$ long protrusions on its inner surface cut out of $\SI{6}{\milli\metre}$ thick acrylic to model the geometry of intestinal villi. Fig.~\ref{fig:3dPrinted} shows an experiment with starting and ending positions drawn with marker on the workspace.

@@

Strips of cow tripe approximately 5mm thick were cut and placed in Neutrally buffered formalin for 24 hours for fixation. After fixation, each sample was transferred to 70\% ethanol for storage. For the experiments, a slice of fixed intestine was attached to the acrylic disc with cyanoacrylate (superglue) and then submerged in corn syrup. A drawback of fixing the tissue samples before experimentation is that they tended to shrivel and dry up a few minutes after being removed from the 70\% ethanol. 
%In using the small intestines, which were about 25mm in diameter, the resulting workspace was less than half of that of our simulated intestines. This meant more care had to be taken in navigating the magnets to their goal locations to avoid getting them too close to each other.

@@

\begin{figure*}\label{fig:3dPrinted}
\centering
\vspace{1.5em}
%\begin{overpic}[width=\columnwidth]{firstImage.jpg}\end{overpic}
\begin{overpic}[width=2\columnwidth]{3dexperiment.pdf}\end{overpic}
\\
\vspace{1em}
\begin{overpic}[width=2\columnwidth]{realTripe.pdf}\end{overpic}
\caption{\label{fig:story}
Positioning particles that receive the same control inputs, but cannot move while a control input pushes them into a boundary.
} \vspace{-1em}
\end{figure*}

>>>>

 The magnetic manipulation system has two pairs of electromagnetic coils each with iron cores at their centers, and arranged orthogonal to each other. The iron core at the center of each coil concentrates the magnetic field towards the workspace. An Arduino and four SyRen regenerative motor drivers were used for control inputs to the coils. Finally, a FOculus F0134SB 659 x 494 pixel camera was attached to the top of the system focusing on the workspace which was back-lit by a $\SI{15}{\watt}$ LED light strip.

@@

The intestine phantom model was used as the first test field of the project and was made to mimic the geometry of an intestine and its villi. The model consists of a circular ring with an outer diameter of $\SI{50}{\milli\metre}$, an inner diameter of $\SI{46}{\milli\metre}$, and 60 $\SI{2}{\milli\metre}$ long protrusions on its inner surface cut out of $\SI{6}{\milli\metre}$ thick acrylic to model the geometry of intestinal villi. Fig.~\ref{fig:story} shows an experiment with starting and ending positions drawn with marker on the workspace.

@@

Strips of cow stomach approximately 5mm thick were cut and placed in neutrally buffered formalin for 24 hours for fixation. After fixation, each sample was transferred to 70\% ethanol for storage. For the experiments, a slice of fixed intestine was attached to the acrylic disc with cyanoacrylate (superglue) and then submerged in corn syrup. A drawback of fixing the tissue samples before experiments is that they tended to shrivel and dry up a few minutes after being removed from the 70\% ethanol. 
%In using the small intestines, which were about 25mm in diameter, the resulting workspace was less than half of that of our simulated intestines. This meant more care had to be taken in navigating the magnets to their goal locations to avoid getting them too close to each other.

@@

\begin{figure*}\label{fig:3dPrinted}
\centering
\vspace{1.5em}
%\begin{overpic}[width=\columnwidth]{firstImage.jpg}\end{overpic}
\begin{overpic}[width=2\columnwidth]{3dexperiment.pdf}\end{overpic}
\\
\vspace{1em}
\begin{overpic}[width=2\columnwidth]{realTripe.pdf}\end{overpic}
\caption{\label{fig:story}
Frames showing particle positions before and after control inputs. Top row: small intestine phantom. Bottom row: cow's stomach tissue.
} \vspace{-1em}
\end{figure*}

### 2018-05-01 journalWallFriction/theory2robAlgs.tex
edited the paper!

To compute the reachable set for a circular workspace, first we consider all possible first contact locations.
 The set of boundary points that a particle can touch before the  other particle  touches is an arc of angle $2(\pi - \frac{\arcsin{d_{12}}}{r})$, where $d_{12}= ||s_1 - s_2||$ and $r$ is the radius of the circle.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{reachableSetCircle.pdf}\end{overpic}
\caption{\label{fig:regionMove}
% the set of points where the red particle is the first to contact the boundary are drawn with a red arc. The  set of points where the blue particle is the first to contact the boundary are drawn with a blue arc. 
Left top: The possible points for the blue and red particles to touch the boundary is shown in blue and red arcs. Left bottom: When the blue particle is touching a wall (blue square) the other particle (red square) can go anywhere in the reachable set (blue region). Right: The $\Delta$ configuration space for the corresponded starting positions of the particles is shown.}
\end{figure}

@@

A circle has an infinite number of sides, thus infinite reachable sets. However, the reachable set can be parameterized by the angle of first contact location $\psi$, as shown in Fig.~\ref{fig:regionMove} where 
%We make the reachable sets by knowing the angle of the chord, $\psi$, shown in Fig.~\ref{fig:psigamma}. Minimum and maximum values of $\psi$ can be calculated in the following equation.
\begin{align}
 \psi \in [\psi_{\min}, \psi_{\max}]= \theta + \Big[\frac{\sin^{-1}{d}}{2r} - \frac{\pi}{2},  \frac{\pi}{2} -\frac{\sin^{-1}{d}}{2r} \Big].
% \psi_{\max} &= \theta -\frac{\alpha}{2} + \frac{\pi}{2}
\end{align}
The possible first contact locations are on an arc with interior angle $\gamma$ parameterized by $\psi$:
\begin{align}\label{eq:ppsi}
p_\psi(\psi) &= r[\cos(\psi ), \sin(\psi )],\\ \label{eq:dprep}
d_\perp(\psi)&= 2 ||(s_1.p_\psi(\psi) - s_2.p_\psi(\psi))||,\\ \label{eq:gamma}
\gamma(\psi) &= \cos^{-1} \Big(1-\frac{d_\perp(\psi)}{r} \Big). 
\end{align} 
Reachable sets with $\pi$ difference in $\psi$ value are equivalent in the  $\Delta$ configuration space, so we can plan in this space and choose between the two options to immobilize the particle closest to a wall. 
The reachable set for any first contact point defined by $\psi$ is the area under a chord from angle $\psi- \frac{\gamma(\psi)}{2}$ to $\psi+ \frac{\gamma(\psi)}{2}$, for a circle of radius $r$ centered at $c = r(\cos(\psi-\pi), \sin(\psi-\pi))$. One such chord is drawn in red in Fig.~\ref{fig:regionMove}.

The equations for the four lines outlining the union of reachable sets are as follows:
\begin{align}\label{eq:circlereachable}
l_1 =  r \Big(&(\cos\psi_{\min}- \cos(\gamma + \psi_{\min}) )\\ \nonumber
 + &(\sin\psi_{\min}- \sin(\gamma + \psi_{\min}))\Big) &  0<\gamma< \gamma(\psi_{\min}),\\ \nonumber
l_2 =  r \Big(&(\cos\psi_{\max}- \cos(\gamma + \psi_{\max}))\\ \nonumber
 + &(\sin\psi_{\max}- \sin(\gamma + \psi_{\max}))\Big) &  \gamma(\psi_{\max})<\gamma< 0,\\  \nonumber
l_3 =  r \Big(&(\cos\psi- \cos( \psi+\gamma(\psi) ) )\\ \nonumber
+ &( \sin\psi-\sin( \psi+ \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max},\\ \nonumber
l_4 =  r \Big(&(\cos\psi- \cos( \psi-\gamma(\psi) ))\\ \nonumber
+ & ( \sin\psi- \sin( \psi- \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max}.\\ \nonumber
\end{align}
We combine these boundaries to compute the reachable set. 
Next, find a $\psi$ that would enable us to reach $\Delta g_c$, the nearest point in the reachable set to $\Delta g$. Eq.~\eqref{eq:ifinchord} checks if an arbitrary point $p$, is in the reachable set corresponding to $\psi$.

\begin{align}\label{eq:ifinchord}
&(p.x - c.x)^2 + (p.y - c.y)^2  > r^2,\\ \nonumber
 &(p_x - c_x) \cos\psi + (p.y- c.y) \sin\psi \leq -r\cdot \cos\gamma.
\end{align}

%Here $c$ is the coordinate of the workspace center and $r$ is the radius of the workspace.
We first check if $\Delta g_c$ is achievable with $\psi_{min}$ and $\psi_{max}$.
 If $\Delta g_c$ is not achievable by $\psi_{\min}$ or $\psi_{\max}$, we draw a line from $\Delta g_c$ and the current relative position, $\Delta s$. This line is a chord of the circle and we find the $\psi$ correspondent to this chord. The following equation finds this $\psi$:
  \begin{equation}
 \psi = \tan^{-1}(\Delta p - \Delta g ).
 \end{equation}

Having $\psi$ enable the particles to achieve $\Delta g_c$ in two moves. One move will cause one robot to touch the wall, the other move will make the required relative position.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{zaxis.pdf}\end{overpic}
\caption{\label{fig:zaxis}
Extending the algorithm to position the particles in 3D.
} %\vspace{-1em}
\end{figure}

>>>>

To compute the reachable set for a circular workspace, first we consider all possible first contact locations.
 The set of boundary points that a particle can touch before the  other particle  touches is an arc of angle $2(\pi - \frac{\arcsin{d_{12}}}{r})$, where $d_{12}= ||s_1 - s_2||$ and $r$ is the radius of the workspace.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{reachableSetCircle.pdf}\end{overpic}
\caption{\label{fig:regionMove}
% the set of points where the red particle is the first to contact the boundary are drawn with a red arc. The  set of points where the blue particle is the first to contact the boundary are drawn with a blue arc. 
Left top: The possible first contact points for the blue and red particles are shown with blue and red arcs. Left bottom: Once the blue particle touches the wall (blue square) the other particle (red square) can go anywhere in the reachable set (red region). Right: The $\Delta$ configuration space for the corresponded starting positions of the particles is shown. The possible reachable sets before contact are shown in the $\Delta$ configuration as a blue region. Once the blue particle contacts the boundary as shown, the reachable $\Delta$ configuration is the red set.}
\end{figure}

@@

A circle has an infinite number of sides, thus infinite reachable sets. However, the reachable set can be parameterized by the angle of first contact location $\psi$, as shown in Fig.~\ref{fig:regionMove} where 
%We make the reachable sets by knowing the angle of the chord, $\psi$, shown in Fig.~\ref{fig:psigamma}. Minimum and maximum values of $\psi$ can be calculated in the following equation.
\begin{align}
 \psi \in [\psi_{\min}, \psi_{\max}]= \theta + \Big[\frac{\sin^{-1}{d}}{2r} - \frac{\pi}{2},  \frac{\pi}{2} -\frac{\sin^{-1}{d}}{2r} \Big].
% \psi_{\max} &= \theta -\frac{\alpha}{2} + \frac{\pi}{2}
\end{align}
The possible first contact locations are on an arc with interior angle $\gamma$ parameterized by $\psi$:
\begin{align}\label{eq:gamma}
\gamma(\psi) &= \cos^{-1} \Big(1-\frac{d_\perp(\psi)}{r} \Big), \textrm{ where:}\\ \label{eq:dprep}
d_\perp(\psi)&= 2 ||(s_1.p_\psi(\psi) - s_2.p_\psi(\psi))||,\\ \label{eq:ppsi}
p_\psi(\psi) &= r[\cos(\psi ), \sin(\psi )].
\end{align} 
Reachable sets with $\pi$ difference in $\psi$ value are equivalent in the  $\Delta$ configuration space, so we can plan in this space and choose between the two options to immobilize the particle closest to a wall. 
The reachable $\Delta$ configuration set for any first contact point defined by $\psi$ is the area under a chord from angle $\psi- \frac{\gamma(\psi)}{2}$ to $\psi+ \frac{\gamma(\psi)}{2}$, for a circle of radius $r$ centered at $c = r(\cos(\psi-\pi), \sin(\psi-\pi))$. One such chord is drawn in red in Fig.~\ref{fig:regionMove}.

The equations for the four lines outlining the union of reachable $\Delta$ configuration sets are as follows:
\begin{align}\label{eq:circlereachable}
l_1 =  r \Big(&(\cos\psi_{\min}- \cos(\gamma + \psi_{\min}) )\\ \nonumber
 + &(\sin\psi_{\min}- \sin(\gamma + \psi_{\min}))\Big) &  0<\gamma< \gamma(\psi_{\min}),\\ \nonumber
l_2 =  r \Big(&(\cos\psi_{\max}- \cos(\gamma + \psi_{\max}))\\ \nonumber
 + &(\sin\psi_{\max}- \sin(\gamma + \psi_{\max}))\Big) &  \gamma(\psi_{\max})<\gamma< 0,\\  \nonumber
l_3 =  r \Big(&(\cos\psi- \cos( \psi+\gamma(\psi) ) )\\ \nonumber
+ &( \sin\psi-\sin( \psi+ \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max},\\ \nonumber
l_4 =  r \Big(&(\cos\psi- \cos( \psi-\gamma(\psi) ))\\ \nonumber
+ & ( \sin\psi- \sin( \psi- \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max}.\\ \nonumber
\end{align}
We combine these boundaries to compute the reachable set summarized in Alg.~\ref{alg:circularReachbale}.
Next, find a $\psi$ that would enable us to reach $\Delta g_c$, the nearest point in the reachable set to $\Delta g$. %Eq.~\eqref{eq:ifinchord} checks if an arbitrary point $p$, is in the reachable set corresponding to $\psi$.
We first check if $\Delta g_c$ is in the $\Delta$ configuration space chords defined by either $\psi_{\min}$ or $\psi_{\max}$ using \ref{eq:ifinchord}.

\begin{align}\label{eq:ifinchord}
&(\Delta g_c.x - c.x)^2 + (\Delta g_c.y - c.y)^2  > r^2 \wedge\\ \nonumber
 &( c.x-\Delta g_c.x ) \cos\psi + ( c.y-\Delta g_c.y) \sin\psi > r\cdot \cos\gamma.
\end{align}

%Here $c$ is the coordinate of the workspace center and $r$ is the radius of the workspace.
%We first check if $\Delta g_c$ is achievable with $\psi_{min}$ and $\psi_{max}$.
 If $\Delta g_c$ is not in either chord, we draw a line from $\Delta g_c$ to the current relative position, $\Delta p$. This line is a chord of the circle centered at $c$. The $\psi$ to this chord obeys:
  \begin{equation}
 \psi = \tan^{-1}(\Delta p - \Delta g_c ).
 \end{equation}

The particles achieve $\Delta g_c$ in two moves. The first move causes one particle to touch the wall, the second move achieves the required relative position.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{zaxis.pdf}\end{overpic}
\caption{\label{fig:zaxis}
Illustration on how boundary contacts enable 3D positioning. Once one particle contacts a boundary, the other particle's reachable set is a prism formed by extending the 2D reachable set in the $z$-direction.
} %\vspace{-1em}
\end{figure}
